---
title: "R Notebook"
output: html_notebook
---



Try executing this chunk by clicking the *Run* button within the chunk or by placing your cursor inside it and pressing *Cmd+Shift+Enter*. 


Add a new chunk by clicking the *Insert Chunk* button on the toolbar or by pressing *Cmd+Option+I*.

When you save the notebook, an HTML file containing the code and output will be saved alongside it (click the *Preview* button or press *Cmd+Shift+K* to preview the HTML file). 

The preview shows you a rendered HTML copy of the contents of the editor. Consequently, unlike *Knit*, *Preview* does not run any R code chunks. Instead, the output of the chunk when it was last run in the editor is displayed.

```{r}

rm(list=ls())
source("TailCausal2023.R")
## Set the directory as where you put this file
setwd("/Users/xyliu/Desktop/Github\ project")

library(crypto2)
library(dplyr)
```


```{r}
# Define the target cryptocurrency symbols that we are interested in analyzing
target_symbols <- c("BTC", "LTC", "XRP", "DOGE", "XLM", "ETH", "TRX", "ADA", "SOL", "DOT")

# Retrieve the list of cryptocurrencies that are currently active
# Then filter to include only those coins that were active at any time during the year 2020
coin_list_2020onwards <- crypto_list(only_active=TRUE) %>% dplyr::filter(first_historical_data<="2020-12-31", last_historical_data>="2020-01-01")

# Identify the indices (row numbers) in the filtered coin list that match the target symbols
indices <- which(coin_list_2020onwards$symbol %in% target_symbols)

print(indices)
```

```{r}
# Download historical daily price data from Jan 1, 2021 to Dec 31, 2024
coins_2021to2024 <- crypto_history(coin_list = coin_list_2020onwards[indices,],
                                   start_date = "2021-01-01", end_date="2024-12-31", interval="1d")
write.csv(coins_2021to2024[,c(4,5,15)], file = "./data/crypto21to24_old.csv")
```

```{r}
# Initialize a tibble with the Date column.
# It extracts the timestamp of BTC rows, slices the first 10 characters (YYYY-MM-DD),
# converts to Date format, and wraps in a tibble.
Cr21to24<-read.csv("./data/crypto21to24_old.csv")
Crmod21to24<-as_tibble(as.Date(substr(as.matrix(Cr21to24 %>% filter(symbol == "BTC") %>% select(timestamp)),1,10))) 


# Loop over each unique symbol and bind its 'close' price to the tibble
for (i in unique(Cr21to24$symbol))
Crmod21to24<-bind_cols(Crmod21to24,Cr21to24 %>% filter(symbol == i) %>% select(close))
colnames(Crmod21to24)<-c("Date",unique(Cr21to24$symbol))
```

```{r}

# Plotting and export to pdf files
# Dont run the code line by line, run the whole block

crypto<-Crmod21to24 %>% select(!(Date))
pre<- "./results/2021to2024/old/"
post<-"21to24"
end1<-"pos.pdf"
end2<-"neg.pdf"
  
cryptopos<-apply(log(crypto),2,diff)   #### high positive return value
cryptoneg<-apply(-log(crypto),2,diff)   #### high negative return value


#acf
mid<-"CrACF"
pdf(paste(pre,mid,post,end1,sep=""),width=20,height=8)
par(mfrow=c(2,5))
for(i in 1:10)
  acf(cryptopos[,i],main=colnames(cryptopos)[i])
dev.off()


pdf(paste(pre,mid,post,end2,sep=""),width=20,height=8)
par(mfrow=c(2,5))
for(i in 1:10)
  acf(cryptoneg[,i],main=colnames(cryptoneg)[i])
dev.off()


# just plot
par(mfrow=c(2,5))  # 2 rows × 5 columns layout
for (i in 1:10) {
  acf(cryptopos[,i], main=colnames(cryptopos)[i])
}

# Plot ACFs of negative log returns
par(mfrow=c(2,5))  # Reset layout before second set
for (i in 1:10) {
  acf(cryptoneg[,i], main=colnames(cryptoneg)[i])
}


## tnum for ETA and DELTA

tnum<-400

# ETA

mid<- "CrETA"

pdf(paste(pre,mid,post,end1,sep=""),width=45,height=25)
par(mfrow=c(5,9))
for(i in 1:9)
{ for (j in (i+1):10)
 PlotETA(cryptopos[,i],cryptopos[,j],t=tnum,cap=paste(colnames(cryptopos)[i],"vs",colnames(cryptopos)[j],sep=" "),ytop=1)
}
 dev.off()
 
 

pdf(paste(pre,mid,post,end2,sep=""),width=45,height=25)
par(mfrow=c(5,9))
for(i in 1:9)
{ for (j in (i+1):10)
 PlotETA(cryptoneg[,i],cryptoneg[,j],t=tnum,cap=paste(colnames(cryptoneg)[i],"vs",colnames(cryptoneg)[j],sep=" "),ytop=1)
}
 dev.off()
 

# Delta 

mid<-"CrDelta"


pdf(paste(pre,mid,post,end1,sep=""),width=45,height=150)
par(mfrow=c(15,3))
for(i in 1:9)
{ for (j in (i+1):10)
 PlotDelta(cryptopos[,i],cryptopos[,j],t=tnum,cap=paste(colnames(cryptopos)[i],"vs",colnames(cryptopos)[j],sep=" "))
}
 dev.off()
 

pdf(paste(pre,mid,post,end2,sep=""),width=45,height=25)
par(mfrow=c(5,9))
for(i in 1:9)
{ for (j in (i+1):10)
 PlotDelta(cryptoneg[,i],cryptoneg[,j],t=tnum,cap=paste(colnames(cryptoneg)[i],"vs",colnames(cryptoneg)[j],sep=" "))
}
 dev.off()
```

